A general and efficient representation of Ancestral Recombination Graphs

### 2023-10-06 paper.tex
Add description of missing box regions in Fig 3

\begin{figure}
\centering
% TODO update the source of this figure to make less tall. It's taking
% up far too much vspace at in native coords at the moment.
\includegraphics[width=\textwidth]{illustrations/ancestry-resolution}
\caption{\label{fig-ancestry-resolution}
Converting the \citet[][Fig.~1]{wiuf1999recombination} example
to a gARG. (A) The original eARG; square nodes represent events, with
each recombination (red) containing a breakpoint.
(B) The corresponding gARG with breakpoints directly converted to
edges annotated with inheritance intervals.
(C) The sample-resolved gARG resulting from simplifying with respect
to the samples, \noderef{a}, \noderef{b}, and \noderef{c}.
Dashed lines show edges that are
no longer present (in practice, nodes \noderef{g}, \noderef{j}, and \noderef{q} would also be removed).
Coalescence with respect to the sample is indicated by shaded bars, as
in Fig~\ref{fig-arg-in-pedigree}A.
Line thickness is proportional to the genomic span of each edge.
Nodes representing recombination events are retained
for clarity, but could be removed by simplification if
desired.
}
\end{figure}

>>>>

\begin{figure}
\centering
% TODO update the source of this figure to make less tall. It's taking
% up far too much vspace at in native coords at the moment.
\includegraphics[width=\textwidth]{illustrations/ancestry-resolution}
\caption{\label{fig-ancestry-resolution}
Converting the \citet[][Fig.~1]{wiuf1999recombination} example
to a gARG. (A) The original eARG; square nodes represent events, with
each recombination (red) containing a breakpoint.
(B) The corresponding gARG with breakpoints directly converted to
edges annotated with inheritance intervals.
(C) The sample-resolved gARG resulting from simplifying with respect
to the samples, \noderef{a}, \noderef{b}, and \noderef{c}.
Dashed lines show edges that are
no longer present (in practice, nodes \noderef{g}, \noderef{j}, and \noderef{q} would also be removed).
Coalescence with respect to the sample is indicated by shaded bars, as
in Fig~\ref{fig-arg-in-pedigree}A; nodes \noderef{n}, \noderef{o}, \noderef{p}, \noderef{q} have incomplete
bars showing that local ancestry of entirely coalesced regions is omitted.
Line thickness is proportional to the genomic span of each edge.
Nodes representing recombination events are retained
for clarity, but could be removed by simplification if
desired.
}
\end{figure}
